RadLib: a radiative property model library for combustion CFD

### 2021-07-19 manuscript/manuscript.tex
edits to section 3 software, and latex compilation

RadLib is an object-oriented C++ library that includes C++, Python, and Fortran interfaces. Upon initial download, the RadLib package contains four subdirectories: \texttt{src} contains the RadLib source code; \texttt{examples} contains instructive example cases, including a simple interface and solver for a parallel planes geometry; \texttt{data} contains ALBDF data tables required for the RCSLW model; and \texttt{docs} contains files used to optionally generate code documentation with Doxygen. An additional directory, \texttt{installed}, is created and populated with RadLib's executables and header files during installation if no other installation location is specified.
The \texttt{src} and \texttt{examples} directories are further divided into \texttt{c++}, \texttt{python}, and \texttt{fortran} subdirectories to differentiate between interfaces. 
%There are three interface options for using this code: C++, Python, and Cython-wrapped Python. 
%C++ interfaces are located within the \texttt{examples/c++} folder, while Python interfaces are located within the \texttt{examples/python} folder. 
%When running examples with Python, the Cython-wrapped version is the default; to run the regular Python version without the Cython wrapper, edit the comments near the top of the example files (i.e \texttt{ex\textunderscore S1.py}). The C++ interface produces the fastest-running code, followed by the Cython-wrapped Python interface and then the regular Python interface.

RadLib installation is automated with CMake as follows. Inside the downloaded \texttt{radlib} folder, the user creates and enters a \texttt{build} directory, then enters the commands \texttt{cmake ..}, followed by \texttt{make}, followed by \texttt{make install}. Project options are specified by editing the top-level \texttt{CMakeLists.txt} file where the options are clearly marked. These can also be specified at the command line. Options include specifying the system installation location, which defaults to \texttt{radlib/installed}; options to build the Python and Fortran interfaces; options to build examples for C++, Python, and fortran; and an option to build the documentation.

The code installation folder includes directories \texttt{include} containing header files and a fortran module file, \texttt{lib} containing library files for each interface, and \texttt{rcslw_data} containing binary data files used by the RCSLW model. These binary files contain the ALBDF functions for a given species at a given pressure (in atm units), as indicated by the file name. The \texttt{include} directory contains the following interface header and module files:
%
\begin{itemize}
    \item \texttt{rad_planck_mean.h},
    \item \texttt{rad_wsgg.h},
    \item \texttt{rad_rcslw.h},
    \item \texttt{rad_module.mod}.
\end{itemize}
%
The C++ and Fortran libraries in the \texttt{lib} folder are
\begin{itemize}
    \item \texttt{libradlib.a},
    \item \texttt{libradlib_fortran.a},
\end{itemize}
%
This folder also contains the python module.
The code installation additionally generates a relocatable CMake package for downstream usage, located at \texttt{build/cmake/radlib/radlib.cmake}. If the Python interface is built, the location of the installed Python package needs to be added to the \texttt{PYTHONPATH} environment variable. A command to do this is provided at the end of the installation (for example, \texttt{export PYTHONPATH="/home/user/radlib/installed/lib/python3.8/site-packages:$PYTHONPATH"}).

To use RadLib in C++, a user code includes the header file for the desired radiation model, e.g., \texttt{#include "rad_rcslw.h"}. For Fortran, a \texttt{use rad_module} statement provides access to the required interface functions. The Python interface functions are loaded from the \texttt{pyrad} module, as in \texttt{from pyrad import pyrad_rcslw}. Such usage is demonstrated in the code examples, discussed below. Compilation of C++ and Fortran programs requires specification of the header/module and library directory locations and linking against the installed libraries (\texttt{libradlib.a} for C++ and both \texttt{libradlib.a} and \texttt{libradlib_fortran.a} for Fortran).

Figure \ref{fig:flowchart} illustrates the basic structure of using of RadLib in a generic one-dimensional RTE solution. The RadLib library generates absorption coefficients and their weighting factors for use within an appropriate RTE solver. A user first creates a radiation object, and then makes calls to one of two primary functions: \texttt{get\textunderscore k\textunderscore a()}, or \texttt{get\textunderscore k\textunderscore a\textunderscore oneband()}.
These two functions take the arguments for temperature (K), pressure (Pa), soot volume fraction, and mole fractions of \ce{H2O}, \ce{CO2}, \ce{CO}, and \ce{CH4}. The WSGG model does not account for \ce{CO} or \ce{CH4}, and only the PM model includes \ce{CH4}. A uniform interface is facilitated by giving default values of 0.0 for the \ce{CO} and \ce{CH4} mole fraction parameters. The \texttt{get\textunderscore k\textunderscore a()} function computes a vector of absorption coefficients and a vector of weight factors, with elements corresponding to each clear and gray gas considered in the model (with the clear gas coming first). The PM model only considers one gas and the vectors are of unity size. The \texttt{get\textunderscore k\textunderscore a\textunderscore oneband()} computes the absorption coefficient and weight factor (as scalar values) for a single gas (or \emph{band}), whose index (starting at zero for all interfaces) is provided as an additional argument. This option to compute the properties for a single gas/band can be important for efficient implementation in some solvers, e.g., in the Fire Dynamics Simulation (FDS), discussed below \cite{FDS}. The absorption coefficients and weights are returned through the function argument list for the C++ and Fortran interfaces, and as return values for the Python interface. Additional details are included in the program documentation and code listing.
%
\begin{figure}
	\begin{center}
        \includegraphics[width=\textwidth]{fig_radlib_structure.pdf}
	\end{center}
	\caption{Example workflow diagram. Highlighted areas are part of the RadLib library; other areas represent example infrastructure for using the package.}
\label{fig:flowchart}
\end{figure}
%

>>>>

RadLib is an object-oriented C++ library that includes C++, Python, and Fortran interfaces. Upon initial download, the RadLib package contains four subdirectories: \texttt{src} contains the RadLib source code; \texttt{examples} contains instructive example cases, including a simple interface and solver for a parallel planes geometry; \texttt{data} contains ALBDF data tables required for the RCSLW model; and \texttt{docs} contains files used to optionally generate code documentation with Doxygen. An additional directory, \texttt{installed}, is created and populated with RadLib's executables and header files during installation if no other installation location is specified.
The \texttt{src} and \texttt{examples} directories are further divided into \texttt{c++}, \texttt{python}, and \texttt{fortran} subdirectories to differentiate between interfaces.

RadLib installation is automated with CMake as follows. Inside the downloaded \texttt{radlib} folder, the user creates and enters a \texttt{build} directory, then enters the commands \texttt{cmake ..}, followed by \texttt{make}, followed by \texttt{make install}. Project options are specified by editing the top-level \texttt{CMakeLists.txt} file where the options are clearly marked. These can also be specified at the command line. Options include specifying the system installation location, which defaults to \texttt{radlib/installed}; options to build the Python and Fortran interfaces; options to build examples for C++, Python, and Fortran; and an option to build the documentation.

The code installation folder includes directories \texttt{include} containing header files and a Fortran module file, 
\texttt{lib} containing library files for each interface, and \texttt{rcslw\textunderscore data} containing binary data files used by the RCSLW model. These binary files contain the ALBDF functions for a given species at a given pressure (in atm units), as indicated by the file name. The \texttt{include} directory contains the following interface header and module (Fortran) files:
%
\begin{itemize}
    \item \texttt{rad\textunderscore planck\textunderscore mean.h},
    \item \texttt{rad\textunderscore wsgg.h},
    \item \texttt{rad\textunderscore rcslw.h},
    \item \texttt{rad\textunderscore module.mod}.
\end{itemize}
%
The C++ and Fortran libraries in the \texttt{lib} folder are
\begin{itemize}
    \item \texttt{libradlib.a},
    \item \texttt{libradlib\textunderscore fortran.a},
\end{itemize}
%
This folder also contains the Python module.
The code installation additionally generates a relocatable CMake package for downstream usage, located at \texttt{build/cmake/radlib/radlib.cmake}. If the Python interface is built, the location of the installed Python package needs to be added to the \texttt{PYTHONPATH} environment variable. A command to do this is provided at the end of the installation, for example, \\ {\scriptsize \texttt{export PYTHONPATH="/home/user/radlib/installed/lib/python3.8/site-packages:\$PYTHONPATH"}}.

To use RadLib in C++, a user code includes the header file for the desired radiation model, e.g., \texttt{\#include "rad\textunderscore rcslw.h"}. For Fortran, a \texttt{use rad\textunderscore module} statement provides access to the required interface functions. The Python interface functions are loaded from the \texttt{pyrad} module, as in \texttt{from pyrad import pyrad\textunderscore rcslw}. Such usage is demonstrated in the code listing for the examples discussed below. Compilation of C++ and Fortran programs requires specification of the header/module and library directory locations and linking against the installed libraries (\texttt{libradlib.a} for C++ and both \texttt{libradlib.a} and \texttt{libradlib\textunderscore fortran.a} for Fortran).

Figure \ref{fig:flowchart} illustrates the basic structure of using of RadLib in a generic one-dimensional RTE solution. The RadLib library generates absorption coefficients and their weighting factors for use within an appropriate RTE solver. A user first creates a radiation object, and then makes calls to one of two primary functions: \texttt{get\textunderscore k\textunderscore a()}, or \texttt{get\textunderscore k\textunderscore a\textunderscore oneband()}.
These two functions take the arguments for temperature (K), pressure (Pa), soot volume fraction, and mole fractions of \ce{H2O}, \ce{CO2}, \ce{CO}, and \ce{CH4}. The WSGG model does not account for \ce{CO} or \ce{CH4}, and only the PM model includes \ce{CH4}. A uniform interface is facilitated by giving default values of 0.0 for the \ce{CO} and \ce{CH4} mole fraction parameters. The \texttt{get\textunderscore k\textunderscore a()} function computes a vector of absorption coefficients and a vector of weight factors, with elements corresponding to each clear and gray gas considered in the model (with the clear gas coming first). The PM model only considers one gas and the vectors are of unity size. The \texttt{get\textunderscore k\textunderscore a\textunderscore oneband()} computes the absorption coefficient and weight factor (as scalar values) for a single gas (or \emph{band}), whose index (starting at zero for all interfaces) is provided as an additional argument. This option to compute the properties for a single gas/band can be important for efficient implementation in some solvers, e.g., in the Fire Dynamics Simulation (FDS), discussed below \cite{FDS}. The absorption coefficients and weights are set through the function argument list for the C++ and Fortran interfaces, and as return values for the Python interface. Additional details are included in the program documentation and code listing.
%
\begin{figure}
	\begin{center}
        \includegraphics[width=\textwidth]{fig_radlib_structure.pdf}
	\end{center}
	\caption{Example workflow diagram. Highlighted areas are part of the RadLib library; other areas represent example infrastructure for using the package.}
\label{fig:flowchart}
\end{figure}
%
